An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-09-21 poly-embed-journal/poly-embed-journal.tex
5.3,5.4

% alphabetical order, by convention
\newcommand{\A}{\mathcal{A}}
\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\renewcommand{\H}{\mathcal{H}}
\newcommand{\I}{\mathcal{I}}
\renewcommand{\L}{\mathcal{L}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\OP}{\mathcal{OP}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Sc}{\mathcal{S}}
\newcommand{\U}{\mathcal{U}}
\newcommand{\V}{\mathcal{V}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

@@

\subsection{Embedding Ordered Partitions via Weston-Watkins Hinge}
\label{sec:winge}
As hinge loss is one of the most common surrogates for binary support vector machines (SVMs), original extensions to the multiclass setting involved a one-vs-all reduction to the binary problem via hinge loss, thus generating ${n \choose 2}$ hyperplanes for $n$ labels.
Proposing a more efficient solution,~\citet{weston1999support} give an alternate surrogate for multiclass SVM prediction, defined as follows for predictions $u \in \reals^n$,
\begin{equation}\label{eq:ww-hinge}
L(u,y) = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
\end{equation}
While it was later shown to be inconsistent~\citep{tewari2007consistency,liu2007fisher}, \citet{dogan2016unified} nonetheless advocate for the Weston-Watkins SVM to be the default for multiclass prediction problems.

\citet*{wang2020weston} use embeddings to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{Ordered Partition} loss, and in turn, show inconsistency with respect to 0-1 loss.
An ordered partition on $[n] := \{1, \ldots, n\}$ can be defined by a nested sequence of tuples $T = \{T_1, \ldots, T_l\}$ with $\emptyset \subsetneq T_1 \subsetneq \ldots \subsetneq T_l = [n]$ for some $l \geq 2$.
The ordered partition target loss $\ell^{\OP}$ is defined by
%An ordered partition on $[n] := \{1, \ldots, n\}$ is an ordered list $S = (S_1, \ldots, S_l)$ of nonempty, pairwise disjoint sets such that $\cup_i S_i = [n]$, and assume $l \geq 2$.
%The ordered partition target loss $\ell^{\OP}$ is defined, for $i \in [n]$ and $S = (S_1, \ldots, S_l) \in \OP_n$ by
\begin{align*}
\ell^\OP(T,y) &= |T_1| - 1 + \sum_{i=1}^{l-1} |T_{i+1}| \cdot \Ind{y \not \in T_i}~.~
\end{align*}
The summation in this ordered partition loss can be interpreted as a variation of 0-1 loss where one can report sets of sets, and increases the punishment for the outcome $y$ not being in the earlier sets in the ordering; outside the summation is a punishment for having a large prediction set on the first $T_1$.
This work presents an embedding for $\ell^\OP$ and uses this fact to show that the Weston-Watkins hinge loss~\citep{weston1999support} is in fact calibrated (and hence consistent) with respect to $\ell^\OP$.
\citet[Definition 2.3]{wang2020weston} takes the embedding $\varphi : \OP_n \to \reals^n$ entrywise so that for all $j \in T_i \setminus T_{i-1}$, we have $\varphi(T)_j = -(i-1)$.

\begin{figure}[H]
	\begin{minipage}{0.5\linewidth}
	\centering
	\includegraphics[width=0.9\linewidth]{tikz/ordered-partition}
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\linewidth}
	\caption{Level sets of $\psi \circ \prop{WW}$, the property elicited by Weston-Watkins hinge with embedding given by~\citet[Definition 2.3]{wang2020weston}.  $\prop{WW}$ is shown with dotted lines.}
	\label{fig:ordered-partition}
	\end{minipage}
\end{figure}

@@

Other hinge-like surrogates are shown to be non-consistent by~\citet{lapin2016loss} and~\citet{yang2018consistency}.
For example, $\psi_2$ from~\citet[Table 1]{yang2018consistency} elicits essentially the same property $\prop{WW}$ shown in Figure~\ref{fig:ordered-partition} before the link is applied for certain values of $n$ and $k$.
\citet{TOPKPAPER} applies the embedding framework to these surrogates to understand the target problems for which they are consistent.

@@

Moreover, \citet{TOPKPAPER} presents an embedding (Eq.~\eqref{eq:topk-embedding}) for top-$k$ loss that looks unlike the commonly studied surrogates in the literature.
Moreover, the most common link $\psi^{\tt argmax}(u) := \argmax_{S \subseteq \Y : |S| = k} \sum_{i \in S} u_i$ is calibrated for the surrogate in Equation~\eqref{eq:topk-embedding}.\jessie{TODO... confirm this is true.}
Their proof uses the $\epsilon$-thickened link construction from \S~\ref{sec:calibration} to understand which choices of linked values are feasible and align these choices with the argmax link.

>>>>

% alphabetical order, by convention
\newcommand{\A}{\mathcal{A}}
\newcommand{\C}{\mathcal{C}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\F}{\mathcal{F}}
\renewcommand{\H}{\mathcal{H}}
\newcommand{\I}{\mathcal{I}}
\renewcommand{\L}{\mathcal{L}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\OP}{\mathcal{OP}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Sc}{\mathcal{S}}
\newcommand{\T}{\mathcal{T}}
\newcommand{\U}{\mathcal{U}}
\newcommand{\V}{\mathcal{V}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\Y}{\mathcal{Y}}

@@

\subsection{Embedding Ordered Partitions via Weston-Watkins Hinge}
\label{sec:winge}
As hinge loss is one of the most common surrogates for binary support vector machines (SVMs), original extensions to the multiclass setting involved a one-vs-all reduction to the binary problem via hinge loss, thus generating ${n \choose 2}$ hyperplanes for $n$ labels.
Proposing a more efficient solution,~\citet{weston1999support} give an alternate surrogate for multiclass SVM prediction, defined as follows for predictions $u \in \reals^n$,
\begin{equation}\label{eq:ww-hinge}
L_{WW}(u,y) = \sum_{i \in \Y : i \neq y} (1 - (u_y - u_i))_+~.~
\end{equation}
While it was later shown to be inconsistent~\citep{tewari2007consistency,liu2007fisher}, \citet{dogan2016unified} nonetheless advocate for the Weston-Watkins SVM to be the default for multiclass prediction problems.

\citet*{wang2020weston} use our embedding framework to construct and prove the calibration of the Weston-Watkins surrogate for the \emph{ordered partition} loss, and in turn, show inconsistency with respect to 0-1 loss\raft{But it was already known, right?  If so, it's good to use phrases like ``recover the result that''}.
%An ordered partition on $[n] := \{1, \ldots, n\}$ can be defined by a nested sequence of tuples
%Let $T = \{T_1, \ldots, T_k\}$
The report space for this discrete loss can be defined in terms of nested subsets of $[n] := \{1, \ldots, n\}$, as follows.%
\footnote{To recover the partition of~\citet{wang2020weston}, one can define $S_i = T_i \setminus T_{i-1}$.}
\begin{align*}
\T = \{ (T_0,\ldots,T_k) \mid k \geq 2, \emptyset = T_0 \subsetneq T_1 \subsetneq \ldots \subsetneq T_k = [n]\}~.
\end{align*}
The ordered partition target loss $\ell^{\OP} : \T \to \reals^\Y_+$ is then defined by
\begin{align*}
\ell^\OP(T,y) &= \sum_{i=1}^{k} |T_{i}| \cdot \Ind{y \not \in T_{i-1}}-1~.~
\end{align*}
\raf{Jessie, could you check that the newer form is correct?  I messed with a couple things, and decided not to clutter the tex with the old stuff -- maybe check the diff if it would help, or go straight to the original version.}

This loss can be interpreted as a variation of 0-1 loss where one reports a nested sequence of sets, and the punishment for the outcome $y$ is the cardinality of the first set containing $y$, plus the cardinality of all smaller sets.
\citet{wang2020weston} use our framework to show that $L_{WW}$ embeds $\ell^\OP$, and thus is calibrated with respect to it\raft{Do they construct a link, or start with the existing one?  If the latter, I'm curious how they show consistency; using our framework, as we now describe in 4, or something else?}.
Specifically, they use the embedding
% \citet[Definition 2.3]{wang2020weston}
$\varphi : \T \to \reals^n$ given by $\varphi(T)_j = -(i-1)$ for all $j \in T_i \setminus T_{i-1}$.
\raf{Here would be a good place to define the link $\psi$, even if informally.}

\begin{figure}[H]
	\begin{minipage}{0.5\linewidth}
	\centering
	\includegraphics[width=0.9\linewidth]{tikz/ordered-partition}
	\end{minipage}
	\hfill
	\begin{minipage}{0.45\linewidth}
	\caption{Level sets of $\psi \circ \prop{L_{WW}}$, the property elicited by Weston-Watkins hinge with embedding given by~\citet[Definition 2.3]{wang2020weston}.  $\prop{L_{WW}}$ is shown with dotted lines.}
	\label{fig:ordered-partition}
	\end{minipage}
\end{figure}

@@

\raf{Take one more pass?  Define the brackets notation.  Feel free to guess at what our results are going to be, and then add margin comments that we should revisit.}
Other hinge-like surrogates are shown to be non-consistent by~\citet{lapin2016loss} and~\citet{yang2018consistency}.
For example, $\psi_2$ from~\citet[Table 1]{yang2018consistency} elicits essentially the same property $\prop{WW}$ shown in Figure~\ref{fig:ordered-partition} before the link is applied for certain values of $n$ and $k$.
\citet{ourtopkpaper} applies the embedding framework to these surrogates to understand the target problems for which they are consistent.

@@

Moreover, \citet{ourtopkpaper} presents an embedding (Eq.~\eqref{eq:topk-embedding}) for top-$k$ loss that looks unlike the commonly studied surrogates in the literature.
Moreover, the most common link $\psi^{\tt argmax}(u) := \argmax_{S \subseteq \Y : |S| = k} \sum_{i \in S} u_i$ is calibrated for the surrogate in Equation~\eqref{eq:topk-embedding}.\jessie{TODO... confirm this is true.}
Their proof uses the $\epsilon$-thickened link construction from \S~\ref{sec:calibration} to understand which choices of linked values are feasible and align these choices with the argmax link.
